---
title: "San Francisco Crime Classification"
output: html_notebook
---

```{r}
train <- read.csv(file="train.csv", na.strings=c(""))
test <- read.csv(file="test.csv", na.strings=c(""))
summary(train)
```
```{r}
library(Amelia)
missmap(train, main = "Missing values vs observed")
```

It seems that here are **no missing values**. Great!
```{r}
# Overall structure
str(train)
```
- There might be certain correlation between the resolution and the type of crime?
- Might have something to do with the day of week?
- Maybe we can regroup crimes to reduce the number of categories? Or just select the top crimes as our focus?
```{r}
# Get to know data types
sapply(train, class)
```
```{r}
# summarize the class distribution
cat_percentage <- prop.table(table(train$Category)) * 100
cbind(freq=table(train$Category), percentage=cat_percentage)
```

```{r}
# Get top crimes
crime_categories_df <- as.data.frame(table(train$Category))
crime_categories_df[with(crime_categories_df, order(-Freq)),]
top_crimes <- head(crime_categories_df[with(crime_categories_df, order(-Freq)),], n=10)
```

```{r}
# Create data for the graph.
x <- top_crimes$Freq
labels <- top_crimes$Var1
piepercent <- round(100*x/sum(x), 1)
# Plot the chart.
pie(x, labels = piepercent, main = "Top 10 Crimes",col = rainbow(length(x)))
legend("right", as.character(labels), cex = 0.8,
   fill = rainbow(length(x)))
```
We can see that **larceny/theft** and non-criminal takes up much of the pie, followed by **non-criminal** and **assult**. '**Other offenses**' also accounts for a large proportion, but it contains ambiguities and lacks information.

Is there a day of week that has significantly more crimes than other days?
The distribution is rather even. But Friday is surely a peak (maybe people consume more after a week's work) while Sunday is a slump (most people stay at home).
```{r}
library(ggplot2)
table(train$Category ,train$DayOfWeek)
g <- ggplot(train, aes(DayOfWeek))
g + geom_bar(aes(fill = Category)) + theme(legend.position="bottom")
```
How does criminal activities change over the years? Does it increase or decrease or stay the same?

```{r}
train$Year <- substring(train$Dates, 1, 4)
train$Month <- substring(train$Dates, 6, 7)
crime_history <- head(as.vector(table(train$Month,train$Year)), -12)
crime_history
crime_ts <- ts(crime_history, frequency=12, start=c(2003,1))
crime_ts 
plot.ts(crime_ts)
```
We can see that the basic trend is declining from 2004 to 2010. Then, crime rate begins to rise until 2014. But noticeably we can clearly observe the seasonality throughout the years. So it's worthwhile to investigate the fluctuation over the months. Maybe some analysis over time-in-a-day would be helpful too. For now let's just decompose the data.
```{r}
crime_components <- decompose(crime_ts)
plot(crime_components)
```
It seems the trend is just what I described, roughly. The seasonal component seems really interesting.
```{r}
train_incomplete <- subset(train, Year != 2015)
tb <- table(train_incomplete$Month, train_incomplete$Category)
df <- data.frame(month=as.integer(row.names(tb)), crime_freq=as.vector(tb), crime_categories=rep(colnames(tb), each=length(row.names(tb))))
# plot
ggplot(data = df, aes(x=month, y=crime_freq)) + geom_line(aes(colour=crime_categories)) + theme(legend.position="left")
```
```{r}
# Create the data for the chart.
tb <- table(train_incomplete$Month, train_incomplete$Category)
v = rowSums(tb)
# Plot the bar chart.
plot(v,type = "o", col = "red", xlab = "Month", ylab = "Crime Frequency",
   main = "Monthly Crime")
```
We can see that, usually December and Feburary has the lowest crime rate (perhaps people feel too cold to leave home). June, July, August have low frequency as well. Crime activities peak in May and October. This pattern is observed by all major categories of crime. 
However, the data of December is significantly lower than the others. Maybe it's because of the lack of data in 2015. *I'll get rid of the data of 2015 when necessary and adjust the previous results.*

Just an example of mapping SF.
```{r}
library(ggplot2)
library(ggmap)
library(maptools)
library(ggthemes)
library(rgeos)
library(broom)
library(dplyr)
library(plyr)
library(grid)
library(gridExtra)
library(reshape2)
library(scales)

plotTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 18,colour = "black"),
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(fill = "grey80", color = "white"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=8),
    axis.text = element_text(size=8),
    axis.title.x = element_text(hjust=1),
    axis.title.y = element_text(hjust=1),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"))
}
 
# And another that we will use for maps
mapTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 18,colour = "black"),
    plot.subtitle=element_text(face="italic"),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    strip.text = element_text(size=12),
    axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(fill = "grey80", color = "white"),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"))
}
 
# Define some palettes
palette_9_colors <- c("#0DA3A0","#2999A9","#458FB2","#6285BB","#7E7CC4","#9A72CD","#B768D6","#D35EDF","#F055E9")
palette_8_colors <- c("#0DA3A0","#2D97AA","#4D8CB4","#6E81BF","#8E76C9","#AF6BD4","#CF60DE","#F055E9")
palette_7_colors <- c("#2D97AA","#4D8CB4","#6E81BF","#8E76C9","#AF6BD4","#CF60DE","#F055E9")
palette_1_colors <- c("#0DA3A0")


# Read in a csv of home sale transactions directly from github.
sf <- read.csv("https://raw.githubusercontent.com/simonkassel/Visualizing_SF_home_prices_R/master/Data/SF_home_sales_demo_data.csv")
 
# We will need to consider Sale Year as a categorical variable so we convert it from a numeric variable to a factor
sf$SaleYr <- as.factor(sf$SaleYr)

# Define the URL of the zipped shapefile
URL <- "https://github.com/simonkassel/Visualizing_SF_home_prices_R/raw/master/Data/SF_neighborhoods.zip"
# Download the shapefile to your working directory and unzip it.
download.file(URL, "SF_neighborhoods.zip")
unzip("SF_neighborhoods.zip")
# Read it into R as a spatial polygons data frame & plot
neighb <- readShapePoly("SF_neighborhoods")
plot(neighb)


# Define the bounding box
bbox <- neighb@bbox

# Manipulate these values slightly so that we get some padding on our basemap between the edge of the data and the edge of the map
sf_bbox <- c(left = bbox[1, 1] - .01, bottom = bbox[2, 1] - .005, 
             right = bbox[1, 2] + .01, top = bbox[2, 2] + .005)
# Download the basemap
basemap <- get_stamenmap(
  bbox = sf_bbox,
  zoom = 13,
  maptype = "toner-lite")

# # Map it
# bmMap <- ggmap(basemap) + mapTheme() + 
#   labs(title="San Francisco basemap")
# bmMap

# Define the bounding box
bbox <- neighb@bbox
 
# Manipulate these values slightly so that we get some padding on our basemap between the edge of the data and the edge of the map
sf_bbox <- c(left = bbox[1, 1] - .01, bottom = bbox[2, 1] - .005, 
             right = bbox[1, 2] + .01, top = bbox[2, 2] + .005)
# Download the basemap
basemap <- get_stamenmap(
  bbox = sf_bbox,
  zoom = 13,
  maptype = "toner-lite")
 
# # Map it
# bmMap <- ggmap(basemap) + mapTheme() + 
#   labs(title="San Francisco basemap")
# bmMap

# 
# prices_mapped_by_year <- ggmap(basemap) + 
#   geom_point(data = sf, aes(x = long, y = lat, color = SalePrice), 
#              size = .25, alpha = 0.6) +
#   facet_wrap(~SaleYr, scales = "fixed", ncol = 4) +
#   coord_map() +
#   mapTheme() + theme(legend.position = c(.85, .25)) +
#   scale_color_gradientn("Sale Price", 
#                         colors = palette_8_colors,
#                         labels = scales::dollar_format(prefix = "$")) +
#   labs(title="Distribution of San Francisco home prices",
#        subtitle="Nominal prices (2009 - 2015)",
#        caption="Source: San Francisco Office of the Assessor-Recorder\n@KenSteif & @SimonKassel")
# prices_mapped_by_year
```
```{r}
train[, c("X", "Y", "Year", "Category")]
crime_location <- data.frame( train[, c("X", "Y", "Year", "Category")] )
crime_location
```
```{r}
# Manipulate these values slightly so that we get some padding on our basemap between the edge of the data and the edge of the map
sf_bbox <- c(left = bbox[1, 1] - .01, bottom = bbox[2, 1] - .005, 
         right = bbox[1, 2] + .01, top = bbox[2, 2] + .005)
# Download the basemap
basemap <- get_stamenmap(
  bbox = sf_bbox,
  zoom = 13,
  maptype = "toner-lite")
 
# Map it
bmMap <- ggmap(basemap) + mapTheme() + 
  labs(title="San Francisco Crime Map")
bmMap + geom_point(data=crime_location, aes(x=X, y=Y, color=Category), size=0.7, alpha=0.3) + theme(legend.position = "right")
```

```{r}
top_crime_map <- crime_location[crime_location$Category %in% as.vector(top_crimes$Var1),]
bmMapTop <- ggmap(basemap) + mapTheme() + 
  labs(title="San Francisco Top Crime Map")
bmMapTop + geom_point(data=top_crime_map, aes(x=X, y=Y, color=Category), size=0.7, alpha=0.3) + theme(legend.position = "right")
```
Although this map is beautiful, it provides us with too much information to be insightful. To get more out of this visualisation, we need to limit the categories to those most 'popular' crimes, or we need to regroup the crime categories.
```{r}
# Map it
bmMap <- ggmap(basemap) + mapTheme() + 
  labs(title="San Francisco basemap")

prices_mapped_by_year <- ggmap(basemap) + 
  geom_point(data = top_crime_map, aes(x = X, y = Y, color = Category), 
             size = .25, alpha = 0.6) +
  facet_wrap(~Year, scales = "fixed", ncol = 4) +
  coord_map() +
  mapTheme() + theme(legend.position = "right") +
  labs(title="Top 10 Crimes in San Francisco",
       subtitle="2003 - 2015")
prices_mapped_by_year
```
Ok anyways... Thanks to Kelvin, I noticed there is a very strong correlation between the Descrition column and the Category column. Some text mining is needed though.
```{r}
#train$Descript
library(tm)
library(wordcloud)
descript <- removeNumbers(removePunctuation(tolower(as.vector(train$Descript)))) 
descript <- removeWords(descript, stopwords("en"))
descript_corpus <- Corpus(VectorSource(train$Descript))
descript_corpus = tm_map(descript_corpus, content_transformer(tolower))
descript_corpus = tm_map(descript_corpus, removeNumbers)
descript_corpus = tm_map(descript_corpus, removePunctuation)
descript_corpus = tm_map(descript_corpus, removeWords, c("the", "and"))
descript_corpus =  tm_map(descript_corpus, stripWhitespace)
descript_dtm <- DocumentTermMatrix(descript_corpus)
descript_dtm <- removeSparseTerms(descript_dtm, 0.975)
findFreqTerms(descript_dtm, 100)
raw_freq = data.frame(sort(colSums(as.matrix(descript_dtm)), decreasing=TRUE))
raw_freq
dim(raw_freq)
freq_words <- rownames(raw_freq)
freq_words
wordcloud(rownames(raw_freq), raw_freq[,1], max.words=100, colors=brewer.pal(1, "Dark2"))
```
```{r}
descript_dtm_tfidf <- DocumentTermMatrix(descript_corpus, control = list(weighting = weightTfIdf))
descript_dtm_tfidf = removeSparseTerms(descript_dtm_tfidf, 0.975)
freq = data.frame(sort(colSums(as.matrix(descript_dtm_tfidf)), decreasing=TRUE))
freq
freq_words <- c(freq_words, rownames(freq))
freq_words <- unique(freq_words)
freq_words
wordcloud(rownames(freq), freq[,1], max.words=100, colors=brewer.pal(1, "Dark2"))
```
Ok, let's try to search for some *keywords* in the descript column that matches the category column.
```{r}
unique_cat <- unique(train$Category)
x <- ""
for(cat in unique(train$Category)) {
  x <- paste(x, cat, sep="|")
}
x <- tolower(substring(x,2)) 
match_count_table <- table(grepl(x, tolower(train$Descript)))
match_count_table
prop.table(match_count_table)
```
So about 20% of the DESCRIPT contains the CATEGORY keywords. **There is a rather strong correlation indeed. This is definitely going to be a feature.**
How about the **holidays**? Let's get some data about the public holiday in San Francisco!!!
```{r}
regular_day <- train
train$Holiday <- "Regular"
# Holidays 
new_year <- regular_day[grepl("[0-9]{4}-01-01", regular_day$Dates),]
train$Holiday[grepl("[0-9]{4}-01-01", train$Dates)] <- "NewYear"
regular_day <- regular_day[!grepl("[0-9]{4}-01-01", regular_day$Dates),]
#Valentine
valentine <- regular_day[grepl("[0-9]{4}-02-14", regular_day$Dates),]
train$Holiday[grepl("[0-9]{4}-02-14", train$Dates)] <- "Valentine"
regular_day <- regular_day[!grepl("[0-9]{4}-02-14", regular_day$Dates),]
#MLK <- # Third Monday in January
#presidents_day <- # Third Monday in Febrary
#easter <- # Arr
#memorial_day <- # Last Monday in May
independence_day <- regular_day[grepl("[0-9]{4}-07-04", regular_day$Dates),]
train$Holiday[grepl("[0-9]{4}-07-04", train$Dates)] <- "Independence"
regular_day <- regular_day[!grepl("[0-9]{4}-07-04", regular_day$Dates),]
#labor_day <- # First Monday in September 
#columbus_day <- # Second Monday in October
veterans_day <- regular_day[grepl("[0-9]{4}-11-11", regular_day$Dates),]
train$Holiday[grepl("[0-9]{4}-11-11", train$Dates)] <- "Veterans"
regular_day <- regular_day[!grepl("[0-9]{4}-11-11", regular_day$Dates),]
#thanks_giving <- #  Fourth Thursday in November
christmas <- regular_day[grepl("[0-9]{4}-12-25", regular_day$Dates),]
train$Holiday[grepl("[0-9]{4}-12-25", train$Dates)] <- "Christmas"
regular_day <- regular_day[!grepl("[0-9]{4}-12-25", regular_day$Dates),]
```
```{r}
library(ggplot2)
new_year_top_crime <- new_year[new_year$Category %in% as.vector(top_crimes$Var1),]
g <- ggplot(new_year_top_crime, aes(Year))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("New Year Crime")
```

```{r}
ind_top_crime <- independence_day[independence_day$Category %in% as.vector(top_crimes$Var1),]
g <- ggplot(ind_top_crime, aes(Year))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("Independence Day Crime")
```
```{r}
veterans_top_crime <- veterans_day[veterans_day$Category %in% as.vector(top_crimes$Var1),]
g <- ggplot(veterans_top_crime, aes(Year))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("Veterans Day Crime")
```

```{r}
christmas_top_crime <- christmas[christmas$Category %in% as.vector(top_crimes$Var1),]
g <- ggplot(christmas_top_crime, aes(Year))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("Christmas Crime")
```
Time to do some averaging...
```{r}
library(matrixStats)
new_year_avg <- colMedians(table(new_year_top_crime$Year, droplevels(new_year_top_crime$Category))) 
valentine_top_crime <- valentine[valentine$Category %in% as.vector(top_crimes$Var1),]
valentine_avg <- colMedians(table(valentine_top_crime$Year, droplevels(valentine_top_crime$Category))) 
ind_day_avg <- colMedians(table(ind_top_crime$Year, droplevels(ind_top_crime$Category)))
veterans_avg <- colMedians(table(veterans_top_crime$Year, droplevels(veterans_top_crime$Category)))
christmas_avg <- colMedians(table(christmas_top_crime$Year, droplevels(christmas_top_crime$Category)))
reg_day_top_crime <- regular_day[regular_day$Category %in% as.vector(top_crimes$Var1),]
reg_day_top_crime$DateOnly <- substring(reg_day_top_crime$Dates, 1, 10)
#reg_day_top_crime$DateOnly
reg_day_avg <- colMedians(table(reg_day_top_crime$DateOnly, droplevels(reg_day_top_crime$Category)))
#reg_day_avg
```
```{r}
holiday_comparison_df <- data.frame(NewYear=new_year_avg, Valentine = valentine_avg, Ind=ind_day_avg, Veterans=veterans_avg, Christmas=christmas_avg, Regular=reg_day_avg)
row.names(holiday_comparison_df) <- sort(top_crimes$Var1)
holiday_comparison_df
```
```{r}
par(xpd=TRUE)
barplot(as.matrix(holiday_comparison_df), main="Crimes in Special Days", col=rainbow(nrow(holiday_comparison_df)), xlab="Special Days", bty='L')
legend("topright",
       legend = sort(top_crimes$Var1), 
       fill = rainbow(nrow(holiday_comparison_df)), cex=0.4)
```
Let's see how the plot varies throughout the 24 hours in a day:
```{r}
crime_time_df <- data.frame(Time=as.POSIXct(substring(train$Dates,12), format="%H:%M:%S"), Category=train$Category)
#ggplot(data=crime_time_df, aes(x=crime_time_df$Time, y=)) + geom_point()
```
Let's see if weekends have more crimes than weekdays.
```{r}
library(ggplot2)
wkday <- train
wkday$Week <- "Weekday"
wkday[wkday$DayOfWeek == "Saturday" | wkday$DayOfWeek == "Sunday",]$Week <- "Weekend"

wkday_df <- (data.frame(Week=wkday$Week, Category=wkday$Category))
wkday_df
g <- ggplot(wkday_df, aes(Week))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("Weekday vs. Weekend") + theme(axis.text.x = element_text(angle=90,hjust=1))

wkday_top_crime <- wkday
wk_table <- table(wkday_top_crime$Week)
#wkday_result <- data.frame(Weekday=table(wkday_top_crime$Category, wkday_top_crime$Week)[,1]/wk_table["Weekday"],
#                          Weekend=table(wkday_top_crime$Category, wkday_top_crime$Week)[,2]/wk_table["Weekend"])
wkday_result <- data.frame(Weekday=table(wkday_top_crime$Category, wkday_top_crime$Week)[,1]/5,
                           Weekend=table(wkday_top_crime$Category, wkday_top_crime$Week)[,2]/2)
     
wkday_result
g + theme(legend.position="right")
par(xpd=TRUE)
barplot(as.matrix(wkday_result), main="Weekdays vs. Weekends", col=rainbow(nrow(wkday_result)), xlab="Day of Week", bty='L')
legend("topright",
       legend = sort(top_crimes$Var1), 
       fill = rainbow(nrow(wkday_result)), cex=0.4)
```
It seems that whether a day is a weekday or a weekend doesn't affect both the category and the quantity of crimes...So criminals doesn't have day-offs! SAD!
Umm common sense tells me that more crimes take place at night than during the day. Let's divide the time into day and night!
```{r}
library(chron)
train$Time <- times(substring(train$Dates,12))
dayNight <- data.frame(Times = times(substring(train$Dates,12)), Cat = train$Category)
breaks <- c(0,6,10,14,18,24)/24
labels <- c("EarlyMorning","Morning","Noon","Afternoon","Evening")
dayNight$ind <- cut(dayNight$Times, breaks, labels, include.lowest = TRUE)
train$TimeInDay <- cut(train$Time, breaks, labels, include.lowest = T)
dayNight
g <- ggplot(dayNight, aes(ind))
g + geom_bar() + geom_bar(aes(fill=Cat)) + ggtitle("Crime in a day") + theme(axis.text.x = element_text(angle=90,hjust=1))
```
```{r}
dayNight <- data.frame(Times = times(substring(train$Dates,12)), Cat = train$Category)
breaks <- c(0,5, 20, 24)/24
labels <- c("Night","Day","Night2")
dayNight$ind <- cut(dayNight$Times, breaks, labels, include.lowest = TRUE)
train$DayNight <- cut(train$Time, breaks, labels, include.lowest = T)
dayNight$ind <- gsub("Night2", "Night", dayNight$ind)
train$DayNight <- gsub("Night2", "Night", train$DayNight)
g <- ggplot(dayNight, aes(ind))
g + geom_bar() + geom_bar(aes(fill=Cat)) + ggtitle("Crime in a day") + theme(axis.text.x = element_text(angle=90,hjust=1))
```

Also, maybe crimes are correlated with seasons? Let's check it out! But again, the incompleteness of the data causes us a lot of trouble and might lead to inaccuracies, so some sort of averaging is needed.
```{r}
seasons <- train
# March, April, May <=> Spring
seasons$Season <- "Spring"
train$Season <- "Spring"
# June, July, August <=> Summer
seasons[seasons$Month == "06" | seasons$Month == "07" | seasons$Month == "08",]$Season <- "Summer"
train[train$Month == "06" | train$Month == "07" | train$Month == "08",]$Season <- "Summer"
# September, October, November <=> Fall
seasons[seasons$Month == "09" | seasons$Month == "10" | seasons$Month == "11",]$Season <- "Fall"
train[train$Month == "09" | train$Month == "10" | train$Month == "11",]$Season <- "Fall"
# December, January, February <=> Winter
seasons[seasons$Month == "12" | seasons$Month == "01" | seasons$Month == "02",]$Season <- "Winter"
train[train$Month == "12" | train$Month == "01" | train$Month == "02",]$Season <- "Winter"
season_df <- (data.frame(Season=seasons$Season, Category=seasons$Category))
g <- ggplot(season_df, aes(Season))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("Crime by Season") + theme(axis.text.x = element_text(angle=90,hjust=1))
```
PdDistrict is still unchecked.
```{r}
area_df <- (data.frame(District=train$PdDistrict, Category=train$Category))
area_df
g <- ggplot(area_df, aes(District))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("Crime by District") + theme(axis.text.x = element_text(angle=90,hjust=1))
```
Let's do some text mining as this is by far the most useful information!
First, deal with synonyms of the cats
```{r}
train$Keyword <- NA
library("xlsx")
library("wordnet")
#setDict("/usr/local/Cellar/wordnet/3.1")
#initDict()
old_cats <- tolower(names(sort(table(train$Category), decreasing=F)))
for (cat in old_cats) {
  origin_cat <- cat
  if (grepl("/", cat)) {
    cat <- strsplit(cat, "/")
    for (word in cat[[1]]) {
      syn_list <- synonyms(word, "NOUN")
      pattern <- paste(syn_list, collapse = "|")
      train$Keyword[grepl(pattern, train$Descript)] <- origin_cat
    }
  } else {
    cat <- removeWords(cat, stopwords("en"))
    cat <- trimws(gsub(" +", " ", cat)) 
    cat <- strsplit(cat, " ")
    for (word in cat[[1]]) {
      patter <- paste(synonyms(word, "NOUN"), collapse = "|")
      train$Keyword[grepl(pattern, train$Descript)] <- origin_cat
    }
  }
}
```
Words with top frequency.
```{r}
# Words in Descript with top frequency
freq_words <- (tolower(freq_words))
remove <- c("FROM", "WITH")
freq_words <- freq_words[!freq_words %in% remove]
for (word in freq_words) {
  train$Keyword[grepl(word, train$Descript)] <- word
}
#freq_words
#freq_words_str <- paste(freq_words, collapse = "|")
#freq_words_str
```
Lastly, perfect matches.
```{r}
library(tm)
library(stringr)
# Preprocess the categories 
train$Descript <- tolower(train$Descript)
old_cats <- tolower(names(sort(table(train$Category), decreasing=F)))
for (cat in old_cats) {
  if (grepl("/", cat)) {
    pattern <- gsub("/", "|", cat)
    #print(cat)
  } else {
    pattern <- removeWords(cat, stopwords("en"))
    pattern <- trimws(gsub(" +", " ", pattern)) 
  }
  train$Keyword[grepl(pattern, train$Descript)] <- cat
}
```
Finally we need to take a look at the resolution...
```{r}
res_df <- data.frame(Resolution = train$Resolution, Category = train$Category)
g <- ggplot(res_df, aes(Resolution))
g + geom_bar() + geom_bar(aes(fill=Category)) + ggtitle("Crime Resolutions") + theme(axis.text.x = element_text(angle=90,hjust=1)) +
  theme(legend.position="right") + theme(legend.text = element_text(size=5))
```
```{r}
colnames(train)[which(names(train) == "Keyword")] <- "Keyword"
prop.table(table(is.na(train$Keyword)))
table(train$Keyword)
unique(train$Keyword)
```
Need to improve...Reduce TRUE values...

